---
title: "Untitled"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyquant)
library(glue)
library(dplyr)
library(viridis)
library(ggplot2)
library(tidyverse)
```

```{r data}
rm(list=ls())
filename <- "C:/Users/alber/Downloads/data.csv/data.csv"
df <- readr:: read_csv(file=filename)
```


```{r Missing data}
library(visdat)
library(naniar)
# maps
vis_dat(df)
# no missing value 
gg_miss_var(df[, 1:20])
gg_miss_var(df[, 21:40])
gg_miss_var(df[, 41:50])

# number missing values in the dataset
total <- sum(is.na(df)==TRUE)

#--------------------------------------------------------
if (total >0) {
  print("There are missing values")
  } else {
    print("There are no missing values")
  }
```

```{r dataset}
#X16, X18, X19, X37, X42, X46, X50, X57, X74, X81
# Select variables 
names <- c("Y","X16", "X18", "X19", "X37", "X42", "X46", "X50", "X57", "X74", "X81")
#--------------------------------------------------------------
# dataset we need
data <- df%>%
  select(`Bankrupt?`,`Net Value Per Share (B)`, `Net Value Per Share (C)`, `Persistent EPS in the Last Four Seasons`, `Debt ratio %`, `Operating profit/Paid-in capital`, `Accounts Receivable Turnover`, `Net Value Per Share (C)`, `Net Worth Turnover Rate (times)`, `Cash/Total Assets`, `Cash Turnover Rate`, `Cash Flow to Liability`)
Y <- data$`Bankrupt?`
#-------------------------
colnames(data) <- names
library(corrplot)
data$Y <- as.numeric(data$Y)
corrplot:: corrplot(cor(data), method="circle")
```

```{r Normalization}
sum_TRUEs <- matrix(1, ncol=ncol(data))
for(j in 1:ncol(data)){
  sum_TRUEs[1,j]= sum((data[,j]>1))
}

#_-------------------------
# Normalization of the data 
nor <-function(x) { (x -min(x))/(max(x)-min(x))   }

data$X42 <- nor(data$X42)

data$X74 <- nor(data$X74)
```
According to Sum_trues variable, there are values greater than 1 in columns 7 (X42) and 10 (X74). Therefore, it is imperative to normalise those columns/columns. 

```{r Generalised Linear Regression}
# We convert bankruptcy to a factor because we treat it as a categorical variable
data$Y <- factor(data$Y)
logit.model2 <- glm(Y~ X16+ X18+ X19+ X37+ X42+ X46+ X50+ X57+ X74+ X81 , data = data, family = 'binomial')

#--------------------------------------------------------------------------
# remove X18 because it is strongly correlated with X16. 
# remove X46 because it is statistically insignificant.
logit.model <- glm(Y~ X16+ X37+ X42+ X50+ X57+ X74+ X81 , data = data, family = 'binomial')
# summary
summary(logit.model)
# Confidence intervals of the regression coefficients. 
confint(logit.model)%>%
  round(digits=4)
```

```{r Preidction}
#
predicted_data <- predict(logit.model)%>%
  data.frame()

colnames(predicted_data)[1] <- "predicted"

df <-cbind(data, predicted_data)
pred_0 <- df%>%
  filter(Y==0)%>% 
  select( predicted)%>%
  mutate(Y=0)
pred_1 <- df%>%
  filter(Y==1)%>% 
  select( predicted)%>%
  mutate(Y=1)
library(data.table)
df1 <- melt(
  rbind(data.table(pred_0), data.table(pred_1)), id.vars="Y"
)

df1%>%
  arrange(value)%>%
  ggplot(., mapping=aes(x=1:nrow(df), y=1/(1+exp(-value)), group=Y, col=Y)) + geom_point(size=1.5) + theme_bw()+ labs(
    x="Index", y="Probability of default", title="Sigmoid Function"
  )

```


```{r Cluster Analysis}
# select the data 
#Use means of each independent predictor grouped by default and non-default firms
non_default_medians<-data[-c(3,6)]%>%
  filter(Y==0)%>%
  .[-c(1)]%>%
  apply(.,2,FUN=median)

default_medians <- data[-c(3,6)]%>%
  filter(Y==1)%>%
  .[-c(1)]%>%
  apply(.,2,FUN=median)

df2 <- rbind(default_medians, non_default_medians)%>%
  cbind(data.frame(Y=c(1,0)), .)

df2%>%
  data.table()%>%
  melt(id.vars="Y")%>%
  ggplot(mapping=aes(x=variable, y=value, group=Y, col=as.factor(Y))) + geom_point()+geom_line() +theme_bw() + labs( y="Median of parameters", x="Predictors", title="Average of predictors", subtitle="Grouped by bankrupt (1) and Non-bankrupt (0) firms")

```
The cash turnover rate of bankrupt firms (1) exceeds that of non-bankrupt ones, indicating that firms with low cash reserves tend to be in financial distress. 
```{r 2 variants}
library(class)
# split data into 80/20
train.ind <- sample(seq_len(nrow(data)), size = floor(0.80*nrow(data)))
bankruptcy.train <- data[train.ind,]
bankruptcy.test <- data[-train.ind,]

glm_model <- glm(
  data=bankruptcy.train, formula=Y~X16+X19+X37+X42+X50+X57+X74+X81, family="binomial"
)
summary(glm_model)
# predict on test
p <- predict(glm_model, bankruptcy.test, type="response")
# if P exceeds a threshold of 0.5,1 else 0
def_or_no_default <- ifelse(p>0.75,1,0)
# convert to factor factor
p_class <- factor(def_or_no_default, levels=levels(bankruptcy.test[["Y"]]))
# create confusion matrix
library(caret)
confusionMatrix(p_class, bankruptcy.test[["Y"]])
#----------------------------------------------------------------------

#OR
 ##run knn function with 5 clusters 
pr <- knn(bankruptcy.train, bankruptcy.test,cl=bankruptcy.train$Y, k=5)

##create confusion matrix
tab <- table(pr,bankruptcy.test$Y)
tab
```
From the confusion matrix we can see there are no false bankruptcies
